The Goldilocks Level of Friction: Using User Numbers, Ratings, and Reviews to Evaluate Digital Self-Control Tools

### 2022-05-09 paper.Rmd
calculate quantiles

```{r, include=FALSE}
(num_reviews_summary <- reviews_w_main_cat_data %>% 
  group_by(tool_id) %>% 
  summarise(num_reviews = n()) %>% 
  summarise(median = median(num_reviews),
            mean = mean(num_reviews),
            min = min(num_reviews),
            max = max(num_reviews),
            IQR = IQR(num_reviews)))

(word_count_summary <- reviews_w_main_cat_data %>% 
  summarise(median = median(review_word_count),
            mean = mean(review_word_count),
            min = min(review_word_count),
            max = max(review_word_count),
            IQR = IQR(review_word_count)))

>>>>

```{r, include=FALSE}
(num_reviews_summary <- reviews_w_main_cat_data %>% 
  group_by(tool_id) %>% 
  summarise(num_reviews = n()) %>% 
  summarise(mean = mean(num_reviews),
            min = quantile(num_reviews, 0),
            q_25 = quantile(num_reviews, 0.25),
            median = quantile(num_reviews, 0.5),
            q_75 = quantile(num_reviews, 0.75),
            max = quantile(num_reviews, 1))

(word_count_summary <- reviews_w_main_cat_data %>% 
  summarise(mean = mean(review_word_count),
            min = quantile(review_word_count, 0),
            q_25 = quantile(review_word_count, 0.25),
            median = quantile(review_word_count, 0.5),
            q_75 = quantile(review_word_count, 0.75),
            max = quantile(review_word_count, 1)))
